% VLDB template version of 2020-08-03 enhances the ACM template, version 1.7.0:
% https://www.acm.org/publications/proceedings-template
% The ACM Latex guide provides further information about the ACM template

\documentclass[sigconf, nonacm]{acmart}

%% The following content must be adapted for the final version
% paper-specific
\newcommand\vldbdoi{XX.XX/XXX.XX}
\newcommand\vldbpages{XXX-XXX}
% issue-specific
\newcommand\vldbvolume{14}
\newcommand\vldbissue{1}
\newcommand\vldbyear{2020}
% should be fine as it is
\newcommand\vldbauthors{\authors}
\newcommand\vldbtitle{\shorttitle} 
% leave empty if no availability url should be set
\newcommand\vldbavailabilityurl{https://github.com/Jakob-L-M/partial-inclusion-dependencies}
% whether page numbers should be shown or not, use 'plain' for review versions, 'empty' for camera ready
\newcommand\vldbpagestyle{plain} 

% added packages
\usepackage[noend,linesnumbered]{algorithm2e}
\usepackage{cleveref}

\SetKwInput{KwInput}{Input}
\SetKwInput{KwOutput}{Output}
\SetKwIF{If}{ElseIf}{Else}{if}{}{else if}{else}{end if}

\begin{document}
\title{Partial Inclusion Dependency Discovery}

%%
%% The "author" command and its associated commands are used to define the authors and their affiliations.
\author{Jakob Leander Müller}
\affiliation{%
  \institution{Philipps-Universität Marburg}
  \streetaddress{P.O. Box 1212}
  \city{Marburg}
  \state{Germany}
  \postcode{35037}
}
\email{muelle5t@students.uni-marburg.de}
\email{me@jakob-l-m.de}

\author{Thorsten Papenbrock}
\orcid{0000-0002-4019-8221}
\affiliation{%
  \institution{Philipps-Universität Marburg}
  \city{Marburg}
  \country{Germany}
}
\email{papenbrock@informatik.uni-marburg.de}


%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In a world where data grows exponentially and data sharing becomes more common, the need for efficient and flexible data profiling increases constantly.  Identifying inclusion dependencies (INDs) among attributes is crucial for tasks like data integration, query optimization, and integrity checking. A significant challenge lies in detecting these relationships, particularly with the increasing size of datasets, which escalates the complexity of IND discovery.
Past research dealing with INDs mostly overlooked the potential of partial INDs (pINDs), meaning imperfect subsets. Such pINDs can enable researchers and data engineers to understand databases, even if different sources do not match perfectly. After introducing pIND properties and discussing new strategies for (p)IND discovery, combining known strategies such as a sort-merge join and heavy parallelization, we will introduce \textit{SPIND}. An algorithm that is not only able to find all pINDs, it also outperforms the current state-of-the-art algorithm \textit{BINDER} in both unary and nary settings by multiple magnitudes.
\end{abstract}

\maketitle

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\pagestyle{\vldbpagestyle}
\begingroup\small\noindent\raggedright\textbf{PVLDB Reference Format:}\\
\vldbauthors. \vldbtitle. PVLDB, \vldbvolume(\vldbissue): \vldbpages, \vldbyear.\\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi}
\endgroup
\begingroup
\renewcommand\thefootnote{}\footnote{\noindent
This work is licensed under the Creative Commons BY-NC-ND 4.0 International License. Visit \url{https://creativecommons.org/licenses/by-nc-nd/4.0/} to view a copy of this license. For any use beyond those covered by this license, obtain permission by emailing \href{mailto:info@vldb.org}{info@vldb.org}. Copyright is held by the owner/author(s). Publication rights licensed to the VLDB Endowment. \\
\raggedright Proceedings of the VLDB Endowment, Vol. \vldbvolume, No. \vldbissue\ %
ISSN 2150-8097. \\
\href{https://doi.org/\vldbdoi}{doi:\vldbdoi} \\
}\addtocounter{footnote}{-1}\endgroup
%%% VLDB block end %%%

%%% do not modify the following VLDB block %%
%%% VLDB block start %%%
\ifdefempty{\vldbavailabilityurl}{}{
\vspace{.3cm}
\begingroup\small\noindent\raggedright\textbf{PVLDB Artifact Availability:}\\
The source code, data, and/or other artifacts have been made available at \url{\vldbavailabilityurl}.
\endgroup
}
%%% VLDB block end %%%

%%% Start of paper content %%%
\input{introduction/introduction}

\input{foundations/related_work}

\input{foundations/definitions}

\input{foundations/dealing_with_null}

\input{pINDs/partial_IND_algorithms}

\input{pINDs/spind}

\input{pINDs/filter}

\input{pINDs/candidate_generation}

\input{results/evaluation}

\input{results/future}

%%% End of paper content %%%

%\clearpage

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample}

\end{document}
\endinput
